IML Term project

### 2022-12-03 main_markdown.rmd

@@

```{r load data}
npf <- read.csv("npf_train.csv")
```

```{r preprocess data}

# Muokataan dataa.

# Luodaan class2
npf$class2 <- factor("event", levels = c("nonevent", "event"))
npf$class2[npf$class4 == "nonevent"] <- "nonevent"

# Tehdään päivämäärästä rivitunniste
rownames(npf) <- npf[, "date"]

# Poistetaan sarakkeet id, date, class4, partlybad
npf <- npf[, -(1:4)]
```

>>>>

# Set-up and data preprosessing

@@

```{r load data}
npfOrig <- read.csv("npf_train.csv")
```

Columns selected by correlation

```{r preprocess data}
# Create class2
npfOrig$class2[npfOrig$class4 == "nonevent"] <- 0
npfOrig$class2[npfOrig$class4 != "nonevent"] <- 1

# Add date as row name
rownames(npfOrig) <- npfOrig[, "date"]

# Select global and 16.8 m high values
npf <- data.frame(npfOrig[, (5:6)], npfOrig[, (13:16)], npfOrig[, (27:30)], 
                  npfOrig[, (41:42)], npfOrig[, (53:54)], npfOrig[, (63:72)],
                  npfOrig[, (83:88)], npfOrig[, (99:104)])

# Calculate the correlation matrix
cm <- cor(npf)

# Order variables by 1st principal component
corrplot(cm, order = "FPC", tl.cex = 0.5, tl.col = "black")
